---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r libraries, echo = TRUE}
library(tidyverse)


```{r read, echo = TRUE}

df_activity <- read.csv("activity.csv", header = TRUE, sep = ",")

```

## What is mean total number of steps taken per day?

```{r histogram1, echo = TRUE}
df_steps <- df_activity %>% 
        group_by(date) %>% 
        summarize(steps= sum(steps, na.rm = TRUE))

hist(df_steps$steps, breaks=8,main = "Total number of steps per day", xlab = "Steps", col = "orange")

mean(df_steps$steps)

median(df_steps$steps)

```

## What is the average daily activity pattern?

```{r time, echo = TRUE}

df_ave <- df_activity %>% 
        group_by(interval) %>% 
        summarize(steps= mean(steps, na.rm = TRUE ))

plot(df_ave$interval,df_ave$steps, 
     type="l", col="red",main="Time series plot of the 5-minute interval \n and the average number of steps taken", 
     xlab = "The 5-minute interval", ylab = "The average number of steps taken")
```

``` {r max, echo = TRUE}
df_ave[which.max(df_ave$steps), ]$interval
```

## Imputing missing values

``` {r strategy, echo = TRUE}
summary(df_activity)

df_activity2 <- df_activity
for (i in 1:nrow(df_activity2))
{
        if (is.na(df_activity2$steps[i])){
                df_activity2$steps[i]<-df_ave[which(df_activity2$interval[i] == df_ave$interval),]$steps
        }
}
summary(df_activity2)
```

``` {r histo2, echo = TRUE}
df_imp <- df_activity2 %>% 
        group_by(date) %>% 
        summarise(steps = sum(steps), na.rm = TRUE)


hist(df_imp$steps, breaks=8,main = "Total number of steps per day", xlab = "Steps", col = "blue")
```

## Are there differences in activity patterns between weekdays and weekends?

``` {r panel, echo = TRUE}
df_activity2$date <- as.Date(df_activity2$date)
df_activity3 <- df_activity2 %>%
        mutate(day = if_else(weekdays(date) %in% c("lördag", "söndag"),
                             "Weekend",
                             "Weekday")) %>% 
        group_by(interval, day) %>% 
        summarise(steps_mean = mean(steps))


ggplot(df_activity3, aes(interval, steps_mean)) + 
        geom_line(color="blue", size=1) + facet_wrap(~day, nrow=2, ncol=1) +
        labs(x="Interval", y="Avg. steps") 
```
